---
title: "Shiny Assignment"
author: Vishweshwaran
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment Instructions

Instructions

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Data set used and Summary of the Data set

Description
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). 

```{r}
summary(mtcars)
```

## Variables and plots

The data frame has 11 variables.

[, 1] mpg Miles/(US) gallon

[, 2] cyl Number of cylinders

[, 3] disp Displacement (cu.in.)

[, 4] hp Gross horsepower

[, 5] drat Rear axle ratio

[, 6] wt Weight (lb/1000)

[, 7] qsec 1/4 mile time

[, 8] vs V/S

[, 9] am Transmission (0 = automatic, 1 = manual)

[,10] gear Number of forward gears

[,11] carb Number of carburetors

```{r, echo=FALSE}
plot(mtcars)
```

## Links

GitHub link
https://github.com/Vishweshwaran/shiny_assignment.git

Shiny Link.
 https://vishweshwaransridhar.shinyapps.io/shiny_assignment/

